Waking up a sleeping rabbit:\\ On Natural-Language Sentence Generation with FF

### 2010-03-01 trunk/Papers/crisp-ff-10/main.tex
intro umgeschrieben, platz gemacht.
final PDF-Ok-according-to-AAAI-standards

\pdfinfo{
/Title (Using Planning to Generate Natural-Language Sentences)
/Subject (Proceedings of ICAPS, hopefully)
/Author (Anonymous authors)}

@@

\begin{document}
\title{Using Planning to Generate Natural-Language Sentences:\\
  Experiences and Challenges}

\author{
Alexander Koller \\ Saarland University, Germany \\ koller@mmci.uni-saarland.de
%\And
%Ronald Petrick \\ University of Edinburgh, UK \\ rpetrick@inf.ed.ac.uk
\And
J\"org Hoffmann \\ INRIA, France \\ joerg.hoffmann@inria.fr
}

@@

\bibliography{bibliography}
\bibliographystyle{aaai}

>>>>

\special{! /pdfmark where
{pop} {userdict /pdfmark /cleartomark load put} ifelse
[ /Author (Alexander Koller, Joerg Hoffmann)
/Title (Waking up a sleeping rabbit: On Natural-Language Sentence Generation with FF)
/Keywords (AAAI, artificial intelligence)
/DOCINFO pdfmark}

%\pdfinfo{
%/Title (Waking up a sleeping rabbit:\\ On Natural-Language Sentence Generation with FF)
%/Subject (Proceedings of ICAPS, hopefully)
%/Author (Anonymous authors)}

@@

\begin{document}
\title{Waking up a sleeping rabbit:\\ On Natural-Language Sentence Generation with FF}

\author{
Alexander Koller \\ Saarland University, Germany \\ koller@mmci.uni-saarland.de
\And
J\"org Hoffmann \\ INRIA, France \\ joerg.hoffmann@inria.fr
}

\nocopyright

@@

{\small
\bibliography{bibliography}
\bibliographystyle{aaai}
}
